The Driving Forces of API Evolution

### 2015-05-25 thesis/paper.tex
adssa

%Codes
To analyse the data each change identified in the spreadsheet was coded based on which module the change occurred in and two other characteristics: a) if the change added, removed or modified functionality, and b) if the change was a cosmetic change or not.
%Concepts
Grouping the codes by module allowed us to form general concepts of change. However, changes that affected multiple modules were classified on their own.
%Categories
These concepts were then grouped into categories based on common patterns between the concepts.
%Theory
These categories were then used to identify the most notable trends in the evolution of the API. These trends were later used as a basis for discussion during the interview.

%RQ1
The trends identified previously were then classified according to the software maintenance types \cite{chapin2001types}. The process followed the decision tree used for classifying the types of software evolution and software maintenance \cite{chapin2001types}. Each of the previously identified trends were given a main type of change and, if appropriate, a secondary type. Main types of change identify the primary motive for a trend, whereas the secondary types are additional motivations for a trend. For example, a trend that consisted of adding a new module would be seen as an enhancive type of change with no secondary type of change. In addition to this, we analysed the trends based on Lehman's Laws, to determine if they applied to the changes made to the API. This material, as well as the results of the interview, were then used as the basis for answering \textbf{RQ1}.

>>>>

%Codes
To analyse the data, each change identified in the spreadsheet was coded based on which module the change occurred in and two other characteristics: a) if the change added, removed or modified functionality, and b) if the change was a cosmetic change or not.
%Concepts
Grouping the codes by module allowed us to form general concepts of change. However, changes that affected multiple modules were classified on their own.
%Categories
These concepts were then grouped into categories based on common patterns between the concepts.
%Theory
These categories were then used to identify the most notable trends in the evolution of the API. These trends were later used as a basis for discussion during the interview.

%RQ1
The trends identified previously were then classified with help of the decision tree used for classifying the types of software evolution and software maintenance \cite{chapin2001types}. Each of the previously identified trends were given a main type of change and, if appropriate, a secondary type. Main types of change identify the primary motive for a trend, whereas the secondary types are additional motivations for a trend. For example, a trend that consisted of adding a new module would be seen as an enhancive type of change with no secondary type of change. In addition to this, we analysed the trends based on Lehman's Laws, to determine if they applied to the changes made to the API. This material, as well as the results of the interview, were then used as the basis for answering \textbf{RQ1}.
